---
title: "Untitled"
output: html_document
date: "2023-11-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(keras)
library(tensorflow)
library(reticulate)
path_to_python <- "/Users/aarya_kulkarni/opt/anaconda3/bin/python3"
virtualenv_create("r-reticulate", python = path_to_python)
install_tensorflow(envname = "r-reticulate")
install_keras(envname = "r-reticulate")
use_virtualenv("r-reticulate")
```

```{r}
root_dir <- rprojroot::find_rstudio_root_file()
data_dir <- file.path(root_dir, "data")
scripts_dir <- file.path(root_dir, "scripts")
results_dir <- file.path(root_dir, "results")

setwd(data_dir)
load("claims-clean-example.RData")
load("claims-raw.RData")
load("claims-clean-header.Rdata")
```

# Partioning data

```{r}
# partition
set.seed(102722)
partitions <- claims_clean %>%
  mutate(text_clean = str_trim(text_clean)) %>%
  filter(str_length(text_clean) > 5) %>%
  initial_split(prop = 0.7)
```

# Creating tf_idf matrix on training data

```{r}
train_dtm <- nlp_fn(training(partitions)) 
```

# Storing training data w/o labels

```{r}
x_train <- train_dtm %>%
  select(-bclass, -.id) %>%
  as.matrix()
```

# extract labels and coerce to binary

```{r}
y_train <- train_dtm %>%
  pull(bclass) %>%
  factor() %>%
  as.numeric() - 1
```

# Creating keras NN

```{r}
model <- keras_model_sequential(input_shape = ncol(x_train)) %>%
  layer_dense(10) %>%
  layer_dense(1) %>%
  layer_activation(activation = 'sigmoid')

summary(model)
```







# Adam optimization is a stochastic gradient descent method that is based on adaptive estimation of first-order and second-order moments.
model %>%
  compile(
    loss = 'binary_crossentropy',
    optimizer = "adam",
    metrics = 'binary_accuracy'
  )

history <- model %>%
  fit(x = x_train,
      y = y_train,
      epochs = 50)

plot(history)

```


